Wrap Around

### 2024-04-06 scripts/00.1_wrapAround.qmd
re-ran models and organized scripts

reps <- 100
shiftMax <- 2
```

@@

# See an example of the deviations for 10 random vultures
vultures <- sample(allMetrics$Nili_id, size = 15)
allMetrics %>% filter(season == "2023_summer", Nili_id %in% vultures) %>%
  ggplot(aes(x = Nili_id, y = wrapped_normDegree))+
  geom_violin()+
  geom_point(aes(x = Nili_id, y = normDegree), col = "firebrick2", size = 2)+
  facet_wrap(~situ, scales = "free")+
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank())
```

@@

metrics_summary %>%
  filter(!is.infinite(z_str)) %>%
  ggplot(aes(x = normDegree, y = z_str, col = situ))+
  geom_point()+
  geom_smooth(method = "lm")+
  theme_minimal()+
  facet_wrap(~season, scales = "free")
```
Interesting that for co-roosting, the relationship between degree and z-score doesn't look the same. Maybe just because the co-roosting distributions are so incredibly left-skewed that everything gets thrown off by the few points that have a lower normDegree? Anyway, what matters is that we are now getting normal z-scores for roosting, not just 0 and 1.

Let's look at the z-score distributions to see if we'll have to change our modeling method or not.
```{r}
metrics_summary %>%
  ggplot(aes(x = z_deg, group = interaction(season, situ), col = situ))+
  geom_density() # these look decently normally distributed, so we should be okay modeling normally.

>>>>

reps <- 100
shiftMax <- 1
```

@@

# See an example of the deviations for 10 random vultures
set.seed(3)
vultures <- sample(allMetrics$Nili_id, size = 15)
allMetrics %>% filter(season == "2023_summer", Nili_id %in% vultures) %>%
  ggplot(aes(x = Nili_id, y = wrapped_normDegree))+
  geom_violin()+
  geom_point(aes(x = Nili_id, y = normDegree), col = "firebrick2", size = 2)+
  facet_wrap(~situ, scales = "free")+
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank())
```

@@

metrics_summary %>%
  filter(!is.infinite(z_str)) %>%
  ggplot(aes(x = normDegree, y = z_str, col = situ))+
  geom_point()+
  geom_smooth(method = "lm")+
  theme_minimal()+
  facet_wrap(~season, scales = "free")
```

Interesting that for co-roosting, the relationship between degree and z-score doesn't look the same. Maybe just because the co-roosting distributions are so incredibly left-skewed that everything gets thrown off by the few points that have a lower normDegree? Anyway, what matters is that we are now getting normal z-scores for roosting, not just 0 and 1.

Let's look at the z-score distributions to see if we'll have to change our modeling method or not.

```{r}
metrics_summary %>%
  ggplot(aes(x = z_deg, group = interaction(season, situ), col = situ))+
  geom_density() # these look decently normally distributed, so we should be okay modeling normally.
